---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "90%"
)
```

# cwtr

<!-- badges: start -->
  [![Project Status: WIP – Initial development is in progress, but there
     has not yet been a stable, usable release suitable for the
     public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
<!-- badges: end -->

This R package allows for simple calculation of CWT estimates 
and bootstrap intervals for tag recovery and sampling in fisheries. 
                                                                 
<br>

## Installation

You can install the development version of cwtr from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("justinpriest/cwtr", build_vignettes = TRUE)
```

<br>

## Example Usage

 cwtr allows you to quickly calculate point estimates using 
 the function `cwtEst()`.  
```{r demopointest}
 library(cwtr) 
 x <- cwtEst(N=c(33666,NA), n=7618, 
             lambda=c(138,140,116,116), m=1, theta=c(0.01886,102.15))
 summary(x) 
```
 
<br> 

The function `cwtBoot()` calculates bootstrapped intervals for
the cwt estimates and can be specified for different methods. 
```{r demoboot}
library(cwtr)
x <- cwtEst(N=c(33666,NA), n=7618, 
            lambda=c(138,140,116,116), m=1, theta=c(0.01886,102.15))
xBoot <- cwtBoot(x, method="parametric", nreps=10000)
summary(xBoot)
```

<br> 

These data are of class `cwt` which allows for simple use 
of the plot method to generate plots of the bootstrap simulation: 
```{r demoplot, fig.height = 5, fig.width = 7}
library(cwtr)
x <- cwtEst(N=c(33666,NA), n=7618, 
            lambda=c(138,140,116,116), m=1, theta=c(0.01886,102.15)) 
xBoot <- cwtBoot(x, method="parametric", nreps=10000)
plot(xBoot) 
```


