---
title: "Chilkat Coho Harvest, Year 2000"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Chilkat_Harvest_2000}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
# Initially created using usethis::use_vignette("Chilkat_Harvest_2000")
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


There are several functions that provide useful calculations of CWT estimates and variances.  
The core function `cwtEst()` takes parameters from the fishery and sample recovery as arguments. 
These are: **_N_** (number of fish harvested), 
**_n_** (number of fish inspected for marks), 
**_m_** (number of marked fish in the sample), 
**_theta_** (proportion of marked fish in the sample population), and
**_lambda_** (a vector of 4 tag recovery numbers).  
Note that the argument for _N_ and _theta_ can be either a single number 
(estimate only) or a vector of both the estimate and the variance.  

# Chilkat Coho Example
The following example uses actual estimates of coho salmon marked in the 
Chilkat River, with tag recovery occurring during the troll fishery in 
stat week 28 for the NW Quadrant.  


## Calculate Estimate & Summary
The function `cwtEst()` uses the fishery and tag recovery parameters as 
arguments. This allows for output of the estimates:  
```{r example1}
library(cwtr)
cwtEst(N=c(33666, NA), n=7618, lambda=c(138, 140, 116, 116), m=1, theta=c(0.01886, 102.15))
```

<br>

Next, we can use the summary method to obtain the SE, CV, and CI for our estimate:
```{r example2}
x <- cwtEst(N=c(33666, NA), n=7618, lambda=c(138, 140, 116, 116), m=1, theta=c(0.01886, 102.15))
summary(x)
```

<br>

## Bootstrap Intervals
Because these are data from a non-normal distribution, we know that at small estimates 
using Gaussian confidence intervals are likely to be incorrect and/or result in 
negative harvest, tags, etc.  
For this reason, a bootstrap interval function is provided:  
```{r example3, fig.height = 5, fig.width = 6}
xBoot <- cwtBoot(x, method="parametric", nreps=10000)
xBoot

```

<br>

As with before, we can obtain the summary of the bootstrap intervals:
```{r example4, fig.height = 5, fig.width = 6}
summary(xBoot)

```

<br>

Last, using the `plot()` function on a cwt object can provide plots of the 
bootstrap simulation.  
```{r example5, fig.height = 4, fig.width = 6}
plot(xBoot)
```


<br>  