---
title: "CWT Example: Geiger 1990"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CWTexample_Geiger1990}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = FALSE}
library(cwtr)
varbinom <- function(p, n) { return( p*(1-p)/(n-1)) }
```
## Parameter Explanation  
To estimate the contribution of tagged fish to a specific harvest, we first must 
know several numbers pertaining to the initial mark application, 
the fishery of interest, and results of the tag recovery process. These values 
include:  
- **_N_**: the number of fish harvested,  
- **_n_**: the number of fish inspected for marks,  
- **_m_**: the number of marked fish in the sample,  
- **_theta_**: the proportion of fish marked during the first marking event 
( __theta__), ranging from 0-1,  
- **_lambda_**:  the tag recovery numbers making up a vector of length four. These
values are 1) the number of heads with CWT shipped to the taglab, *A1* or *a*, 
2) the number of heads received by the taglab, *A2* or *a'*, 
3) the number of tags detected at the taglab, *M1*, and 
4) the number of tags successfully decoded, *M2*.  


## Calculating Point Estimates
For the first code demonstration, we replicate the first example from Geiger 
(1990). In a fishery of interest, 50% of the run was externally marked and 
applied a coded wire tag. During the fishery, 1000 fish were harvested; 
of these, 200 were randomly selected to be inspected for marks. 
This sample revealed 10 marks. Of these marks, 1 head was sent to the tag lab 
and received, where the tag was detected and successfully decoded.  

Inputting these parameters into the function `cwtEst()` allows for a simple
calculation of the point estimate:  

```{r geigerex1}
x <- cwtEst(N=c(1000,NA), n=200, lambda=c(1,1,1,1), m=10, theta=c(0.5,NA))
x 
```


In addition, we are also interested in the summary statistics of the point
estimate, potentially at varying alpha levels:  
```{r geigerex2 }
summary(x, alpha=0.2)
```


## Calculating Bootstrap Intervals 
#Calculate the simulated distribution  
#Summary statistics from the Bootstrap method

```{r geigerex3 }

xBoot <- cwtBoot(x, method="geiger", nreps=10000)
xBoot

summary(xBoot, alpha=0.2)
```


```{r geigerex4, fig.height = 4, fig.width = 6}
#Figure 1
hist(xBoot$Bootstrap$r.boot, xlim = c(0,200)); abline(v=100, lwd=3, col="red")
```


## Example: Geiger's 'P known' example
For this example, we replicate the calculation of Geiger's 'P known' example, 
across a variety of tags found in the sample. Consider how the estimates and 
bootstrap intervals change across each tag recovery level.  
```{r geigerex5, fig.height = 8, fig.width = 6}
x8  <- cwtEst(N=c(1000,NA), n=200, lambda=c(1,1,1,1), m=8 , theta=c(0.5,NA))
x12 <- cwtEst(N=c(1000,NA), n=200, lambda=c(1,1,1,1), m=12, theta=c(0.5,NA))
x15 <- cwtEst(N=c(1000,NA), n=200, lambda=c(1,1,1,1), m=15, theta=c(0.5,NA))
#Bootstrap Estimates
xBoot8  <- cwtBoot(x8 , method="geiger", nreps=10000)
xBoot12 <- cwtBoot(x12, method="geiger", nreps=10000)
xBoot15 <- cwtBoot(x15, method="geiger", nreps=10000)
#Figure 2
par(mfrow=c(3,1))
hist(xBoot8$Bootstrap$r.boot , xlim = c(0,300), main="2a"); abline(v=80,  lwd=3, col="red")
hist(xBoot12$Bootstrap$r.boot, xlim = c(0,300), main="2b"); abline(v=120, lwd=3, col="red")
hist(xBoot15$Bootstrap$r.boot, xlim = c(0,300), main="2c"); abline(v=150, lwd=3, col="red")
```

To calculate the SE for this product, we use a simple function `varbinom()` 
(not included in this package) to calculate the variance, using the formula:  
$$ \frac{p(1-p)}{(n-1)} $$
```{r geigerex6}
sqrt(varbinom(  5/10,  10))
sqrt(varbinom( 25/50,  50))
sqrt(varbinom(50/100, 100))
```


## Example: Geiger's 'P is Estimated' Example

As a final example, we calculate contribution estimates for where p has been
estimated. This is more common in wild populations. 

```{r geigerex7, fig.height = 4, fig.width = 6}
#Point Estimates for Geiger's 'P is Estimated' example
x    <- cwtEst(N=c(1000,NA), n=200, lambda=c(1,1,1,1), m=10, theta=c(0.5,NA))
x10  <- cwtEst(N=c(1000,NA), n=200, lambda=c(1,1,1,1), m=10, theta=c(0.5,0.167))
x50  <- cwtEst(N=c(1000,NA), n=200, lambda=c(1,1,1,1), m=10, theta=c(0.5,0.071))
x100 <- cwtEst(N=c(1000,NA), n=200, lambda=c(1,1,1,1), m=10, theta=c(0.5,0.050))
#Summary statistics 
summary(x   , alpha=0.2)
summary(x10 , alpha=0.2)
summary(x50 , alpha=0.2)
summary(x100, alpha=0.2)
#"Hack" the cwt object to reproduce the P estimated example in geiger
x10$InputData$theta[2]  = 10
x50$InputData$theta[2]  = 50
x100$InputData$theta[2] = 100
#Bootstrap Estimates
xBoot    <- cwtBoot(x   , method="geiger", nreps=1000)
xBoot10  <- cwtBoot(x10 , method="geiger", nreps=1000)
xBoot50  <- cwtBoot(x50 , method="geiger", nreps=1000)
xBoot100 <- cwtBoot(x100, method="geiger", nreps=1000)
#Summary statistics
summary(xBoot   , alpha=0.1)
summary(xBoot10 , alpha=0.1)
summary(xBoot50 , alpha=0.2)
summary(xBoot100, alpha=0.2)
#Figure 3
par(mfrow=c(3,1))
hist(xBoot10$Bootstrap$r.boot , xlim = c(0,300), main="3a"); abline(v=100, lwd=3, col="red")
hist(xBoot50$Bootstrap$r.boot , xlim = c(0,300), main="3b"); abline(v=100, lwd=3, col="red")
hist(xBoot100$Bootstrap$r.boot, xlim = c(0,300), main="3c"); abline(v=100, lwd=3, col="red")

```

